Stay in shape! Homework exam II

### 2016-03-31 geometricAlgorithms/homeworkExam/2/homeworkExam.tex
added algorithm and extended the proof

\begin{enumerate}[i]
	\item \emph{There is no disk that has its centor non the $x$ axis
			that lies inside all half-planes.}

		$C_i$ never crosses the x axis,
		so it exists entirely above or below $y=0$. Or the intersection is empty.

@@

			\If{$h_i$ is parallel to the x-axis}
				\State
				\Return $False$
			\EndIf
			\State
			\Comment{Check where the x axes crossings are, and write it into
			a variable pair, if both pairs are filled its not case ii.}
			\If{$h_i$ points left}
			\State
				$b_r \gets h_i$
			\EndIf
			\If{$h_i$ points right}
			\State
				$b_l \gets h_i$
			\EndIf
			\If{$b_r$ not equal to $None$ and $b_l$ not equal to $None$}
				\State
				\Return $False$
			\EndIf
		\EndFor
		\State
		\Return $True$
	\EndFunction
\end{algorithmic}
\subsection{Formulate and proof the RIC lemma}
%TODO: een beeetje overtypen van 4.5
Let $1 \leq i \leq n$, let $C_i$ be the defined as above and let $d_i$ be
the largest disk in $C_i$. Then we have
\begin{enumerate}[i]
	\item If $d_{i-1} \in h_{i},$ $then$ $d_i = d_{i-1}$
	\item If $d_{i-1} \in h_{i},$ $then$ $d_i = d_{i-1}$
\end{enumerate}

\subsection{Give the RIC algorithm}

>>>>

\begin{enumerate}[(i)]
	\item \emph{There is no disk that has its centor non the $x$ axis
			that lies inside all half-planes.}

		$C_i$ does not intersect the x axis. So its either an empty set or entirly above or below the x axis.

@@

			\If{$h_i$ is parallel to the x-axis}
				\State
				\Return $False$
			\EndIf
			\State
			\Comment{Check where the x axes crossings are, and write it into
			a variable pair, if both pairs are filled its not case ii.}
			\If{$h_i$ points left}
			\State
				$b_r \gets h_i$
			\EndIf
			\If{$h_i$ points right}
			\State
				$b_l \gets h_i$
			\EndIf
			\If{$b_r$ not equal to $None$ and $b_l$ not equal to $None$}
				\State
				\Return $False$
			\EndIf
		\EndFor
		\State
		\Return $True$
	\EndFunction
\end{algorithmic}
\subsection{Formulate and proof the RIC lemma}
\paragraph{Lemma}
Let $1 \leq i \leq n$, let $C_i$ be the defined as above and let $d_i$ be
the largest disk in $C_i$. Then we have
\begin{enumerate}[(i)]
	\item If $d_{i-1} \subset h_i,$ $then$ $d_i = d_{i-1}$
%TODO: C = nill? dat klopt volgens mij niet
	\item If $d_{i-1} \not\subset h_{i},$ $then$ $C_i$ does not intersect the x-axis
		or $b_i \cap l_i \neq \emptyset$ where $b_i$ is the boundary of $d_i$ and $l_i$
		is the line bounding $h_i$.
\end{enumerate}
\paragraph{Proof}
\newpage
\begin{enumerate}[(i)]
	\item Let $d_{i-1} \subset h_i$. Because $C_i = C_{i-1}\cap h_i$ and
		$d_{i-1} \subset C_{i-1}$ this means that $d_{i-1} \subset C_i$.
		Furtheremore,the optimal disk in $C_i$
		cannot be better than the optimal disk in $C_{i-1}$, since
		$C_i \subseteq C_{i-1}$. Hence, $d_{i-1}$ is the optimal disk
		in $C_i$ as well.
%TODO: replace with using a line between center(d_{i-1}) and
%		center(d_i) then reason about how d_i will keep growing
%		 until it hits h_i.
	\item Let $d_{i-1} \not\subset h_{i}$. Suppose for a contradiction that
		$C_i$ intersects the x-axis and that $b_i \cap l_i = \emptyset$.
		Consider the linesegment $s$ between $center(d_i)$ and 
		$center(d_{i-1})$.
		Where $center$ is a function that returns the center vertex of a disk.
		We have $d_{i-1} \subset C_{i-1}$ and
		since $C_i \subseteq C_{i-1}$, also $d_i \subset C_{i-1}$.
		Together with the convexity of $C_{i-1}$, this implies that
		the line segment $s$ is contained within $C_{i-1}$.
		Since $d_{i-1}$ is the optimal disk in $C_{i-1}$ and the optimum is to
		maximize $r_i$ the radius of $d_i$. Consider $d_i$
		where $s$ is maximized, now to increase $r_i$ we move $d_i$ along $s$,
		we can keep doing this until $b_i \cap h_i$.
		So $d_i$ needs to intersect $h_i$ otherwise $d_i$ is not the optimum
		disk in $C_i$. This shows it cannot be the case that $C_i$ intersects
		the x-axis and $b_i\cap l_i = \emptyset$.

\end{enumerate}
\subsection{Give the RIC algorithm}

\begin{algorithmic}[1]
	\Function{calulateBiggestDisk}{$H$}
		\State
		$d_0 \gets arbitrarlyLargeDisk()$
		\If{hasArbitrarlylargeDisc($H$)}
			\State
			\Return $d_0$
		\EndIf
		\State
		$H_r \gets$ random shuffle $H$
		\For{$i\gets 1$ to $n$ with $h_i \in H_r$}
			\State
			$d_i \gets d_{i-1}$
			\If{$d_{i-1} \not\in h_i$}
				$d_i \gets$
			\EndIf
		\EndFor
	\EndFunction
\end{algorithmic}
